A Mechanical Formalization of Higher-Ranked Polymorphic Type Inference

### 2019-02-11 sections/Overview.tex

%-------------------------------------------------------------------------------
\subsection{Small-Step Unification} Mention some algorithms for unification for 
dependent types that use a small-step approach. Credit them later for some ideas that 
we also employ.

>>>>

%-------------------------------------------------------------------------------
\subsection{Small-Step Unification}
% Mention some algorithms for unification for 
% dependent types that use a small-step approach. Credit them later for some ideas that 
% we also employ.
There are literals that make use of small-step unification for dependently typed
inference and reconstruction algorithms~\cite{}.
These approaches collect a list of constraints and process one at a time.
Similar to DK's algorithm, unification variables are used to represent the types to guess.
In order to solve unification variables to correctly scoped types
(typically constrained by the context when the variable is introduced),
the context information should be kept with the variables.
Judgments that represent unifications of terms might also require such a context
to keep the constraint collection well-formed.
